Supermassive black holes and their host spheroids \\ III. The $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation

### 2016-03-07 papers/mbhn/mbhn.tex
conclusions ellicular

%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  

@@

{\bf Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 

@@

than the $AICc$ value for a single power-law model. }

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
\caption{\bf Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend in the top panel).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
Regardless of the linear regression routine used, 
the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends 
in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
{\bf The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
than the $AICc$ value for a double power-law model. } \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
\caption{\bf Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Conclusions} 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, constitutes a direct measure 
of its central radial concentration of stars. 
After \cite{graham2001bulges} proved that the central black hole mass, $M_{\rm BH}$, 
correlates with the stellar light concentration of a galaxy's spheroidal component, 
\cite{grahamdriver2007} presented and analyzed for the first time a tight $M_{\rm BH} - n_{\rm sph}$ correlation 
using a sample of 27 elliptical and disk galaxies for which they had performed photometric bulge/disk decomposition. 
The $M_{\rm BH} - n_{\rm sph}$ correlation can be predicted from the combination of two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $M_{\rm BH} - L_{\rm sph}$ (e.g.~\citealt{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}) 
and the $L_{\rm sph} - n_{\rm sph}$ (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}). 
However, upon independently attempting photometric multicomponent decompositions 
for galaxy samples that were similar to that used by \cite{grahamdriver2007}, 
three subsequent studies \citep{sani2011,vika2012,beifiori2012} failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ relation. 
\cite{savorgnan2013} collected and compared the S\'ersic index measurements obtained by \cite{grahamdriver2007}, 
\cite{sani2011}, \cite{vika2012} and \cite{beifiori2012}, 
and argued that the discrepancies were due to inaccurate galaxy decompositions. \\
Moved by a urgent need to re-investigate and refine several black hole mass scaling relations, 
we performed state-of-the-art photometric multicomponent decompositions 
(i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
for 66 galaxies with a dynamical measurement of their black hole mass (\emph{Paper I}). 
We carefully measured the S\'ersic index of each galaxy's spheroidal component 
and estimated its associated uncertainty with a method that takes into account statistical and systematic errors. 
Our analysis shows that early- (elliptical + lenticular) and late-type (spiral) galaxies define two different correlations 
in the $L_{\rm sph} - n_{\rm sph}$ diagram, 
whereas they reunite in a single sequence in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
With the current dataset, we measured an amount of intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram systematically smaller, 
but still consistent within the errors, with that observed in the the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). \\ 
%Although we refrain from the conclusion that the $M_{\rm BH} - n_{\rm sph}$ relation is more fundamental than the $M_{\rm BH} - L_{\rm sph}$, 
Our results suggest that the black hole mass is intimately connected to the spheroid central concentration of stars, 
which reflects the inner gradient of the spheroid gravitational potential. 
Besides conferring the spheroid S\'ersic index a predictive power to infer the black hole mass 
from a galaxy's image only (even photometrically uncalibrated), 
the $M_{\rm BH} - n_{\rm sph}$ correlation should become a fundamental ingredient in semi-analytic models and simulations of galaxy formation.

@@

% & \multicolumn{6}{l}{$MAG_{\rm sph}/{\rm [mag]} = \alpha + \beta \bigl(\log n_{\rm sph,eq} - \langle \log n_{\rm sph,eq} \rangle \bigr)$} \\ [0.5em]
%
% All (62)		 & BCES $(Y|X)$ 	      & $-23.88 \pm 0.15$ & $-7.04 \pm 0.89$ & $0.50$ & $-$ & $1.19$ \\
%			 & mFITEXY $(Y|X)$	      & $-23.95 \pm 0.12$ & $-6.43 \pm 0.41$ & $0.50$ & $0.55^{+0.16}_{-0.10}$ & $0.96$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-23.91 \pm 0.14$ & $-6.04 \pm 0.54$ & $0.50$ & $0.75 \pm 0.13$ & $1.07$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-23.88 \pm 0.14$ & $-6.73 \pm 0.48$ & $0.50$ & $-$ & $1.14$ \\
%			 & mFITEXY $(X|Y)$	      & $-23.93 \pm 0.13$ & $-7.13 \pm 0.48$ & $0.50$ & $0.58^{+0.17}_{-0.12}$ & $1.21$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-23.93 \pm 0.15$ & $-7.14 \pm 0.57$ & $0.50$ & $0.76 \pm 0.16$ & $1.21$ \\ [0.5em]
%			 & BCES Bisector	      & $-23.88 \pm 0.15$ & $-6.88 \pm 0.62$ & $0.50$ & $-$ & $1.17$ \\
%			 & mFITEXY Bisector	      & $-23.94 \pm 0.13$ & $-6.76 \pm 0.31$ & $0.50$ & $-$ & $1.15$ \\
%			 & {\tt linmix\_err} Bisector & $-23.92 \pm 0.15$ & $-6.55 \pm 0.40$ & $0.50$ & $-$ & $1.12$ \\ [0.5em]
%
%
% Elliptical (30)	 & BCES $(Y|X)$ 	      & $-25.46 \pm 0.26$ & $4.92 \pm 4.72$ & $0.77$ & $-$ & $1.46$ \\
%			 & mFITEXY $(Y|X)$	      & $-25.66 \pm 0.24$ & $-12.65 \pm 2.78$ & $0.77$ & $0.42^{+0.38}_{-0.42}$ & $1.27$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-25.55 \pm 0.26$ & $-8.54 \pm 4.68$ & $0.77$ & $0.80 \pm 0.24$ & $1.20$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-25.46 \pm 0.40$ & $-20.83 \pm 11.31$ & $0.77$ & $-$ & $2.26$ \\
%			 & mFITEXY $(X|Y)$	      & $-25.63 \pm 0.31$ & $-16.13 \pm 4.37$ & $0.77$ & $0.48^{+0.48}_{-0.48}$ & $1.80$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-25.63 \pm 0.43$ & $-16.66 \pm 6.50$ & $0.77$ & $1.22 \pm 0.65$ & $1.85$ \\ [0.5em]
%			 & BCES Bisector	      & $-25.46 \pm 0.20$ & $-0.08 \pm 0.10$ & $0.77$ & $-$ & $1.14$ \\
%			 & mFITEXY Bisector	      & $-25.65 \pm 0.28$ & $-14.18 \pm 2.43$ & $0.77$ & $-$ & $1.63$ \\
%			 & {\tt linmix\_err} Bisector & $-25.58 \pm 0.35$ & $-11.30 \pm 4.34$ & $0.77$ & $-$ & $1.38$ \\ [0.5em]
%
%\tableline 
%\tableline
%\end{tabular}
%\end{table*}
%
%\begin{table*}
%\centering
%\caption{Linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ diagram.}
%\begin{tabular}{llccccc}
%\tableline
%\tableline
%{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol \langle \log n_{\rm sph} \rangle$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
%\tableline 
%\\
%
% Lenticular (11)	 & BCES $(Y|X)$ 	      & $-22.08 \pm 0.89$ & $16.29 \pm 24.44$ & $0.29$ & $-$ & $3.25$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.16 \pm 0.20$ & $-5.84 \pm 1.83$ & $0.29$ & $0.31^{+0.28}_{-0.20}$ & $0.61$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.08 \pm 0.20$ & $-7.40 \pm 1.27$ & $0.29$ & $-$ & $0.72$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.11 \pm 0.28$ & $-8.30 \pm 3.33$ & $0.29$ & $0.40^{+0.33}_{-0.35}$ & $0.77$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.08 \pm 0.30$ & $0.04 \pm 0.05$ & $0.29$ & $-$ & $1.08$ \\
%			 & mFITEXY Bisector	      & $-22.14 \pm 0.25$ & $-6.86 \pm 1.70$ & $0.29$ & $-$ & $0.70$ \\
%			 & {\tt linmix\_err} Bisector & $$ & $$ & $0.29$ & $$ & $$ \\ [0.5em]
%
%
% Spiral (17)		 & BCES $(Y|X)$ 	      & $-22.33 \pm 0.62$ & $-14.53 \pm 71.43$ & $0.17$ & $-$ & $2.71$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.37 \pm 0.27$ & $-6.53 \pm 2.84$ & $0.17$ & $0.47^{+0.52}_{-0.39}$ & $0.95$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-22.35 \pm 1.23$ & $-3.62 \pm 21.94$ & $0.17$ & $0.63 \pm 0.25$ & $0.93$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.33 \pm 0.35$ & $-7.91 \pm 5.53$ & $0.17$ & $-$ & $1.54$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.74 \pm 0.56$ & $-14.91 \pm 10.03$ & $0.17$ & $0.65^{+1.41}_{-0.65}$ & $2.82$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-22.66 \pm 0.88$ & $-16.17 \pm 21.34$ & $0.17$ & $1.47 \pm 2.15$ & $3.04$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.33 \pm 0.44$ & $-10.25 \pm 18.84$ & $0.17$ & $-$ & $1.94$ \\
%			 & mFITEXY Bisector	      & $-22.48 \pm 0.44$ & $-9.10 \pm 3.31$ & $0.17$ & $-$ & $1.75$ \\
%			 & {\tt linmix\_err} Bisector & $-22.41 \pm 1.07$ & $-5.98 \pm 28.65$ & $0.17$ & $-$ & $1.24$ \\ [0.5em]
%
%
% Early-type (43)	 & BCES $(Y|X)$ 	      & $-24.55 \pm 0.22$ & $-10.81 \pm 1.96$ & $0.64$ & $-$ & $1.46$ \\
%			 & mFITEXY $(Y|X)$	      & $-24.70 \pm 0.14$ & $-7.89 \pm 0.63$ & $0.64$ & $0.46^{+0.18}_{-0.14}$ & $0.93$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-24.63 \pm 0.18$ & $-7.34 \pm 0.83$ & $0.64$ & $0.75 \pm 0.16$ & $1.02$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-24.55 \pm 0.16$ & $-8.35 \pm 0.68$ & $0.64$ & $-$ & $1.10$ \\
%			 & mFITEXY $(X|Y)$	      & $-24.69 \pm 0.16$ & $-8.65 \pm 0.73$ & $0.64$ & $0.48^{+0.20}_{-0.15}$ & $1.14$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-24.68 \pm 0.20$ & $-8.68 \pm 0.91$ & $0.64$ & $0.77 \pm 0.20$ & $1.14$ \\ [0.5em]
%			 & BCES Bisector	      & $-24.55 \pm 0.18$ & $-9.42 \pm 1.00$ & $0.64$ & $-$ & $1.23$ \\
%			 & mFITEXY Bisector	      & $-24.69 \pm 0.15$ & $-8.25 \pm 0.48$ & $0.64$ & $-$ & $1.10$ \\
%			 & {\tt linmix\_err} Bisector & $-24.65 \pm 0.19$ & $-7.96 \pm 0.62$ & $0.64$ & $-$ & $1.07$ \\ [0.5em]
%
%
% Bulge (30)		 & BCES $(Y|X)$ 	      & $-22.25 \pm 0.50$ & $-16.91 \pm 33.45$ & $0.23$ & $-$ & $2.85$ \\
%			 & mFITEXY $(Y|X)$	      & $-22.21 \pm 0.14$ & $-4.25 \pm 0.94$ & $0.23$ & $0.45^{+0.21}_{-0.13}$ & $0.75$ \\
%			 & {\tt linmix\_err} $(Y|X)$  & $-22.23 \pm 0.17$ & $-3.36 \pm 1.62$ & $0.23$ & $0.61 \pm 0.17$ & $0.87$ \\ [0.5em]
%			 & BCES $(X|Y)$ 	      & $-22.25 \pm 0.23$ & $-7.56 \pm 1.94$ & $0.23$ & $-$ & $1.30$ \\
%			 & mFITEXY $(X|Y)$	      & $-22.23 \pm 0.22$ & $-8.20 \pm 2.44$ & $0.23$ & $0.63^{+0.31}_{-0.19}$ & $1.39$ \\
%			 & {\tt linmix\_err} $(X|Y)$  & $-22.22 \pm 0.28$ & $-8.42 \pm 4.00$ & $0.23$ & $0.96 \pm 0.54$ & $1.43$ \\ [0.5em]
%			 & BCES Bisector	      & $-22.25 \pm 0.31$ & $-10.46 \pm 7.05$ & $0.23$ & $-$ & $1.75$ \\
%			 & mFITEXY Bisector	      & $-22.22 \pm 0.19$ & $-5.62 \pm 0.99$ & $0.23$ & $-$ & $1.05$ \\
%			 & {\tt linmix\_err} Bisector & $-22.23 \pm 0.23$ & $-4.84 \pm 1.75$ & $0.23$ & $-$ & $0.98$ \\ [0.5em]

%All (xx)		& BCES $(Y|X)$  	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY $(Y|X)$	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%			& BCES $(X|Y)$  	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY $(X|Y)$	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%			& BCES Bisector 	     & $$ & $$ & $$ & $$ & $$ \\
%			& mFITEXY Bisector	     & $$ & $$ & $$ & $$ & $$ \\
%			& {\tt linmix\_err} Bisector & $$ & $$ & $$ & $$ & $$ \\ [0.5em]
%

@@

  \tableline 
  \tableline
  \end{tabular}
  \label{tab:intsc} 
  %\tablecomments{  }
  \end{table*}

>>>>

@@

Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 

@@

than the $AICc$ value for a single power-law model.

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend in the top panel).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
Regardless of the linear regression routine used, 
the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends 
in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
than the $AICc$ value for a double power-law model.  \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

\section{Conclusions} 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, constitutes a direct measure 
of its central radial concentration of stars. 
After \cite{graham2001bulges} proved that the central black hole mass, $M_{\rm BH}$, 
correlates with the stellar light concentration of a galaxy's spheroidal component, 
\cite{grahamdriver2007} presented and analyzed for the first time a tight $M_{\rm BH} - n_{\rm sph}$ correlation 
using a sample of 27 elliptical and disk galaxies for which they had performed photometric bulge/disk decomposition. 
The $M_{\rm BH} - n_{\rm sph}$ correlation can be predicted from the combination of two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $M_{\rm BH} - L_{\rm sph}$ (e.g.~\citealt{kormendyrichstone1995,magorrian1998,marconihunt2003,haringrix2004}) 
and the $L_{\rm sph} - n_{\rm sph}$ (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}). 
However, upon independently attempting photometric multicomponent decompositions 
for galaxy samples that were similar to that used by \cite{grahamdriver2007}, 
three subsequent studies \citep{sani2011,vika2012,beifiori2012} failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ relation. 
\cite{savorgnan2013} collected and compared the S\'ersic index measurements obtained by \cite{grahamdriver2007}, 
\cite{sani2011}, \cite{vika2012} and \cite{beifiori2012}, 
and argued that the discrepancies were due to inaccurate galaxy decompositions. \\
Moved by a urgent need to re-investigate and refine several black hole mass scaling relations, 
we performed state-of-the-art photometric multicomponent decompositions 
(i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, depleted core, etc.) 
for 66 galaxies with a dynamical measurement of their black hole mass (\emph{Paper I}). 
We carefully measured the S\'ersic index of each galaxy's spheroidal component 
and estimated its associated uncertainty with a method that takes into account statistical and systematic errors. 
Our analysis shows that early- (elliptical + lenticular) and late-type (spiral) galaxies define two different correlations 
in the $L_{\rm sph} - n_{\rm sph}$ diagram, 
whereas they reunite in a single sequence in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
With the current dataset, we measured an amount of intrinsic scatter in the $M_{\rm BH} - n_{\rm sph}$ diagram systematically smaller, 
but still consistent within the errors, with that observed in the the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). \\ 
Our results suggest that the black hole mass is intimately connected to the spheroid central concentration of stars, 
which reflects the inner gradient of the spheroid gravitational potential. 
Besides conferring the spheroid S\'ersic index a predictive power to infer the black hole mass 
from a galaxy's image only (even photometrically uncalibrated), 
the $M_{\rm BH} - n_{\rm sph}$ correlation should become a fundamental ingredient in semi-analytic models and simulations of galaxy formation.

@@

@@

  \tableline 
  \tableline
  \end{tabular}
  \label{tab:intsc} 
  \end{table*}
